Digital Humanities - Ashoka University

### 2021-10-14 Submission.Rmd
Fixing typos

The novels of F. Scott Fitzgerald contain more emotion than the novels of Earnest Hemingway.

@@

We undertook a comparative study of Ernest Hemingway and F. Scott Fitzgerald’s novels. The corpus was created based on availability. Hemingway's works were not on available on Gutenberg, and had to be obtained from a different resource. The files thus obtained were not clean, and contained textual artifacts. The files were cleaned thoroughly so as to prevent issues in analysis. Since Fitzgerald has only 4 finished novels, we obtained 4 novels of Hemingway as well. But the word count differed drastically, so we added Hemingway's _Garden of Eden_ to reach desirable balance in wordcount.

@@

In qualitative reading of literature, it is easy to question what it means for one text to be more emotional than another. One may argue that even simple descriptive paragraphs have emotion attached to them. But it is important to note that our tools are only equipped tell us which author’s work is more overtly emotional: that is, which author’s work will let us decipher emotion without having to analyse subtext or metaphors. Close reading may or may not corroborate our findings, and lack of emotion in our findings definitely does not mean that an author employs less emotion in his writing.

@@

As the graph indicates, Fitzgerald work has a higher percentage of these emotion words. His least emotional novel, _The Great Gatsby_, with only _2.5%_ of the words matching our lexicon, is still higher than Hemingway's most emotional novel -- _A Farewell To Arms_, which stands at _2.1%_. _The Old Man and The Sea_ has the lowest score of the corpus.

>>>>

The novels of F. Scott Fitzgerald contain more emotion than the novels of Ernest Hemingway.

@@

We undertook a comparative study of Ernest Hemingway and F. Scott Fitzgerald’s novels. The corpus was created based on availability. Hemingway's works were not available on Gutenberg, and had to be obtained from a different resource. The files thus obtained were not clean, and contained textual artifacts. The files were cleaned thoroughly so as to prevent issues in analysis. Since Fitzgerald has only 4 finished novels, we obtained 4 novels of Hemingway as well. But the word count differed drastically, so we added Hemingway's _Garden of Eden_ to reach desirable balance in wordcount.

@@

In qualitative reading of literature, it is easy to question what it means for one text to be more emotional than another. One may argue that even simple descriptive paragraphs have emotion attached to them. But it is important to note that our tools are only equipped to tell us which author’s work is more overtly emotional: that is, which author’s work will let us decipher emotion without having to analyse subtext or metaphors. Close reading may or may not corroborate our findings, and lack of emotion in our findings definitely does not mean that an author employs less emotion in his writing.

@@

As the graph indicates, Fitzgerald's work has a higher percentage of these emotion words. His least emotional novel, _The Great Gatsby_, with only _2.5%_ of the words matching our lexicon, is still higher than Hemingway's most emotional novel -- _A Farewell To Arms_, which stands at _2.1%_. _The Old Man and The Sea_ has the lowest score of the corpus.
